G\"{o}del's God on the Computer (Abstract)\thanks{This work has been supported by the German Research Foundation under grant BE2501/9-1.}

### 2013-11-04 Abstract/IWIL-2013/abstract.tex
Abstract for IWIL
more press links

\title{G\"{o}del's God on the Computer\thanks{This work has been
    supported by the German Research Foundation under grant
    BE2501/9-1.}}

@@

In our ongoing computer-assisted study of G\"odel's proof the proof
tools have made some interesting observations, some of which were 
unknown so far.

This work attests the maturity of contemporary interactive and
automated deduction tools for classical higher-order logic and
demonstrates the elegance and practical relevance of the
embeddings-based approach.  Most importantly, our work opens new
perspectives for a computer-assisted theoretical philosophy.  The
critical discussion of the underlying concepts, definitions and axioms
remains a human responsibility, but the computer can assist in
building and checking rigorously correct logical arguments. In case of
logico-philosophical disputes, the computer can check the disputing
arguments and partially fulfill Leibniz' dictum: Calculemus --- Let us
calculate!

>>>>

\title{G\"{o}del's God on the Computer (Abstract)\thanks{This work has been
    supported by the German Research Foundation under grant
    BE2501/9-1.}}

@@

In our ongoing computer-assisted study of G\"odel's proof, the
automated reasoning tools have made some interesting observations,
some of which were unknown so far. This attests the maturity of
contemporary interactive and automated deduction tools for classical
higher-order logic and demonstrates the elegance and practical
relevance of the embeddings-based approach.  Most importantly, our
work opens new perspectives for a computer-assisted theoretical
philosophy.  The critical discussion of the underlying concepts,
definitions and axioms remains a human responsibility, but the
computer can assist in building and checking rigorously correct
logical arguments. In case of logico-philosophical disputes, the
computer can check the disputing arguments and partially fulfill
Leibniz' dictum: Calculemus --- Let us calculate!
